Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-10-26 Paper.tex
Links to smart contract and transactions

A more recent project like Hot-spot me!\cite{hotspotme}
and also very aligned with the technological demonstration
described in this document consist on using mobile
APIs to allow users to share WiFi hot-spot tethering
to users nearby in exchange for ETH supported by a
micro-payment channel contract.

@@

%% \begin{center}
%% %\begin{figure}[h]
%% %  \centering
%%   \includegraphics[keepaspectratio, width=0.481125\textwidth]{images/ethcurrentprice-sourcecoinbase.eps}
%% %  \caption{Figura 3. Variación cotización ETH (11/08/2019)}
%% %\end{figure}
%% \\
%% Figure 7. ETH Price chart (11/08/2019). Source: [Coinbase 19]
%% \\
%% \end{center}

@@

%% \section{Repositorio}\label{sec:repository}
%% El código fuente generado en el proyecto está publicado en un repositorio público de GitHub bajo licencia MIT.
%% \newline\newline
%% \url{https://github.com/ethereum-internet-access}
%% \newline
\begin{thebibliography}{9}
\bibitem{spectrumnh}
  \href{https://uk5g.org/media/uploads/resource_files/Spectrum\_NH\_discussion\_paper\_20Feb19.pdf}{5G Spectrum and Neutral Hosting}, Discussion paper, February 2019,
  DCMS Phase 1 5G Testbeds \& Trials Program
\bibitem{5g} \href{https://en.wikipedia.org/wiki/5G}{https://en.wikipedia.org/wiki/5G}
\bibitem{sdns} Ian F. Akyildiz and Shih-Chun Lin and Pu Wang,
  \textit{Wireless software-defined networks (W-SDNs) and network function virtualization (NFV) for 5G cellular systems:
    An overview and qualitative evaluation}, Computer Networks, 93, 2015
\bibitem{nfv} Jose Ordonez-Lucena et al.
  \textit{Network Slicing for 5G with SDN/NFV: Concepts, Architectures, and Challenges},
   IEEE Communications Magazine ( Volume: 55 , Issue: 5 , May 2017 )
\bibitem{fon} \href{https://es.wikipedia.org/wiki/La_Fonera}{https://es.wikipedia.org/wiki/La\_Fonera}
\bibitem{hotspotme} \href{https://devpost.com/software/hotspot-me}{https://devpost.com/software/hotspot-me}
\bibitem{hostapd} \href{https://w1.fi/hostapd/}{https://w1.fi/hostapd/}
\bibitem{iptables} \href{https://linux.die.net/man/8/iptables}{https://linux.die.net/man/8/iptables}
\bibitem{dnsmasq} \href{https://en.wikipedia.org/wiki/Dnsmasq}{https://en.wikipedia.org/wiki/Dnsmasq}
\bibitem{osmc} \href{https://osmc.tv/}{https://osmc.tv/}

@@

\bibitem{express}
  \href{https://expressjs.com/}{https://expressjs.com/}
\bibitem{mocha}
  \href{https://mochajs.org/}{https://mochajs.org/}
\bibitem{chai}
  \href{https://chaijs.org/}{https://chaijs.org/}

\bibitem{5gcity} \href{https://www.5gcity.eu/}{https://www.5gcity.eu/}
\bibitem{allen}  \href{http://www.lifewithalacrity.com/2016/04/the-path-to-self-soverereign-identity.html}
  {C. Allen, The path to self sovereign identity, 2016}
\bibitem{identicat}
  \href{https://www.coindesk.com/catalonia-government-to-build-dlt-based-identity-platform-for-citizens}
       {Catalonia to Build DLT Identity, Coindesk, 2019}

\bibitem{Coinbase19} Coinbase. Intercambio de moneda digital \href{https://www.coinbase.com/price/ethereum}{https://www.coinbase.com/price/ethereum}
\bibitem{ConsenSys19} Ethereum Smart Contract Best Practices. Security tools. ConsenSys. 12 Agosto 2019.
\bibitem{Docker19} Docker Documentation. How nodes work. 6 Septiembre 2019.  \href{https://docs.docker.com/engine/swarm/how-swarm-mode-works/nodes/}{Docker Swarm}
\bibitem{ETHBerlinZwei19} Hackathon ETH Berlín Zwei. Twitter. 6 Septiembre 2019. \href{https://twitter.com/ETHBerlin}{https://twitter.com/ETHBerlin}
\bibitem{Hegedus18} P. Hegedus. "Towards Analyzing the Complexity Landscape of Solidity Based Ethereum Smart Contracts". 2018 IEEE/ACM 1st International Workshop on Emerging Trends in Software Engineering for Blockchain (WETSEB). 27 Mayo-3 Junio 2018. \href{https://ieeexplore.ieee.org/document/8445056}{https://ieeexplore.ieee.org/document/8445056}
\bibitem{MakerDAO19} MakerDAO. Stability for the blockchain.  \href{https://makerdao.com/en/dai}{https://makerdao.com/en/dai}
\bibitem{Munoz18} J. L. Muñoz. "Docker Containers". Apuntes de las clases magistrales. Máster en Tecnologías Blockchain. 1, Edición. UPC School. 29 Noviembre 2018.
\bibitem{Nakamoto08} S. Nakamoto. "Bitcoin: A Peer-to-Peer Electronic Cash System". 31 Octubre 2008.  \href{https://bitcoin.org/bitcoin.pdf}{https://bitcoin.org/bitcoin.pdf}
\bibitem{RaspberryPi19} Raspberry Pi 3 Modelo B - Placa Base (1,2 GHz Quad-Core Arm Cortex-A53, 1 GB RAM, USB 2.0). Amazon. 11 Agosto 2019.
\bibitem{RaspberryPiBuy19} Raspberry Pi FAQs. BUYING AND SHIPPING. Where can I buy a Raspberry Pi?. Página Web oficial. 11 Agosto 2019.  \href{https://www.raspberrypi.org/help/faqs/#buyingWhere}{https://www.raspberrypi.org/help/faqs/\#buyingWhere}
\bibitem{Stallings04} W. Stallings. "Comunicaciones y redes de computadores". 1 Septiembre 2004. Páginas 904. Pearson Prentice Hall. ISBN-13: 978-8420541105.

\bibitem{berec16} Report on OTT services. BEREC (Body of European Regulators for Electronic Communications). January 2016.
\bibitem{eecc18} [EECC 18] Directive (EU) 2018/1972 of the European
  Parliament and of the Council of 11 December 2018 establishing the
  European Electronic Communications Code (Recast)Text with EEA
  relevance. PE/52/2018/REV/1.

\bibitem{gdpr16} [GDPR 16] Regulation (EU) 2016/679 of the European
  Parliament and of the Council of 27 April 2016 on the protection of
  natural persons with regard to the processing of personal data and
  on the free movement of such data, and repealing Directive 95/46/EC
  (General Data Protection Regulation) (Text with EEA relevance).

\bibitem{h202018} [H2020 18] Ethics and data protection. European
  Commission (DG Research and Innovation). 14 November 2018.

\bibitem{tata17} [Tata 17] A Systematic Approach to Ensuring GDPR
    Compliance: Key Action Items for Telecom Operators. White
    Paper. Tata Consultancy Services. 2017.

\bibitem{neutral} Enabling Neutral Host
Network Economics: CCS case study, GSM Association, August, 2018
\end{thebibliography}
\clearpage

>>>>

A more recent project like Hotspot me!\cite{hotspotme}
and also very aligned with the technological demonstration
described in this document consist on using mobile
APIs to allow users to share WiFi hot-spot tethering
to users nearby in exchange for ETH supported by a
micro-payment channel contract.

@@

\section{Repository}\label{sec:repository}

Recommendations for further study as well as all of the source code generated in the project are also provided.
\newline\newline
Source code published in GitHub (public software repository) under MIT license:
\newline\newline
\href{https://github.com/ethereum-internet-access}{https://github.com/ethereum-internet-access}
\newline\newline
A demo video subtitled is available at the following address on YouTube:
\newline\newline
\href{https://www.youtube.com/watch?v=C9pVMn-pu_8&hd=1}{YouTube video demo}

\begin{center}
%\begin{figure}[h]
%  \centering
  \includegraphics[keepaspectratio, width=0.5\textwidth]{images/maxresdefault.eps}
%  \caption{Figura 2. Raspberry Pi 3 Modelo B. Fuente: [Raspberry 18]}
%\end{figure}
\\
Figure 10. A demo video screenshot.
\\
\end{center}
\vspace{0.15cm}
Finally, the following address on Etherscan shows the Ethereum transactions done:
\newline\newline

\begin{itemize}

\item \href{https://ropsten.etherscan.io/address/0x41b301c0b0abbfeef99803c23a281712e29b6ef1}{The contract itself}

\item \href{https://ropsten.etherscan.io/tx/0xe7aaa957e331475228e613c406a10fa25c0493d8f7d48a9384e4fbe81c36276d}{First demo transaction} (\textit{opening})
\item \href{https://ropsten.etherscan.io/tx/0xa38c0b765718955eb4bcc4e1029cbb538d314305f6a2aa37c2c0c4923f5895cf}{Second demo transaction} (\textit{closing})
\item \href{https://ropsten.etherscan.io/tx/0x0e89290f278d2cc67f38133ce336c38bc0f7689d074e6ac6d39658119bb9c201}{Third demo transaction} (\textit{opening})
\item \href{https://ropsten.etherscan.io/tx/0x89e1db8e0c4798e04d72623cc966a95bf63550c4382eb20f92f11fcbccc4d7cb}{Fourth demo transaction} (\textit{closing})
\end{itemize}
%% \begin{center}
%% %\begin{figure}[h]
%% %  \centering
%%   \includegraphics[keepaspectratio, width=0.481125\textwidth]{images/ethcurrentprice-sourcecoinbase.eps}
%% %  \caption{Figura 3. Variación cotización ETH (11/08/2019)}
%% %\end{figure}e
%% \\
%% Figure 7. ETH Price chart (11/08/2019). Source: [Coinbase 19]
%% \\
%% \end{center}

@@

%% \section{Repositorio}\label{sec:repository}
%% El código fuente generado en el proyecto está publicado en un repositorio público de GitHub bajo licencia MIT.
%% \newline\newline
%% \url{https://github.com/ethereum-internet-access}
%% \newline
\begin{thebibliography}{9}

\bibitem{spectrumnh}
  \href{https://uk5g.org/media/uploads/resource_files/Spectrum\_NH\_discussion\_paper\_20Feb19.pdf}{5G Spectrum and Neutral Hosting}, Discussion paper,
  DCMS Phase 1 5G Testbeds \& Trials Program. February 2019.
\bibitem{5g} \href{https://en.wikipedia.org/wiki/5G}{https://en.wikipedia.org/wiki/5G}
\bibitem{sdns} Ian F. Akyildiz and Shih-Chun Lin and Pu Wang.
  \textit{Wireless software-defined networks (W-SDNs) and network function virtualization (NFV) for 5G cellular systems:
    An overview and qualitative evaluation}. Computer Networks, 93, 2015
\bibitem{nfv} J. Ordonez-Lucena, P. Ameigeiras, D. Lopez, J. J. Ramos-Munoz, J. Lorca and J. Folgueira.
  \textit{Network Slicing for 5G with SDN/NFV: Concepts, Architectures, and Challenges}.
   IEEE Communications Magazine, volume 55, issue 5, May 2017.
\bibitem{fon} \href{https://es.wikipedia.org/wiki/La_Fonera}{https://es.wikipedia.org/wiki/La\_Fonera}
\bibitem{hotspotme} \href{https://devpost.com/software/hotspot-me}{https://devpost.com/software/hotspot-me}
\bibitem{hostapd} \href{https://w1.fi/hostapd/}{https://w1.fi/hostapd/}
\bibitem{iptables} \href{https://linux.die.net/man/8/iptables}{https://linux.die.net/man/8/iptables}
\bibitem{dnsmasq} \href{https://en.wikipedia.org/wiki/Dnsmasq}{https://en.wikipedia.org/wiki/Dnsmasq}
\bibitem{osmc} \href{https://osmc.tv/}{https://osmc.tv/}

@@

\bibitem{express}
  \href{https://expressjs.com/}{https://expressjs.com/}
\bibitem{mocha}
  \href{https://mochajs.org/}{https://mochajs.org/}
\bibitem{chai}
  \href{https://chaijs.com/}{https://chaijs.com/}

\bibitem{5gcity} \href{https://www.5gcity.eu/}{https://www.5gcity.eu/}
\bibitem{allen}  \href{https://github.com/ChristopherA/self-sovereign-identity/blob/master/ThePathToSelf-SovereignIdentity.md}
  {C. Allen.} The Path to Self-Sovereign Identity. GitHub. 25 April 2016.
\bibitem{identicat}
  \href{https://www.coindesk.com/catalonia-government-to-build-dlt-based-identity-platform-for-citizens}
       {D. Palmer.} Catalonia to Build DLT-Based Identity Platform for Citizens. Coindesk. 9 September 2019.

\bibitem{Coinbase19} Ethereum Price (ETH). Coinbase. \href{https://www.coinbase.com/price/ethereum}{https://www.coinbase.com/price/ethereum}
\bibitem{ConsenSys19} Ethereum Smart Contract Best Practices. Security tools. ConsenSys. 12 August 2019.
\bibitem{Docker19} Docker Documentation. How nodes work. 6 September 2019.  \href{https://docs.docker.com/engine/swarm/how-swarm-mode-works/nodes/}{Docker Swarm}
\bibitem{ETHBerlinZwei19} Hackathon ETH Berlin Zwei. 6 September 2019. \href{https://ethberlinzwei.com/}{https://ethberlinzwei.com/}
\bibitem{Hegedus18} P. Hegedus. \textit{Towards Analyzing the Complexity Landscape of Solidity Based Ethereum Smart Contracts}. 2018 IEEE/ACM 1st International Workshop on Emerging Trends in Software Engineering for Blockchain (WETSEB). 27 May-3 June 2018. \href{https://ieeexplore.ieee.org/document/8445056}{https://ieeexplore.ieee.org/document/8445056}
\bibitem{MakerDAO19} MakerDAO. Stability for the blockchain.  \href{https://makerdao.com/en/dai}{https://makerdao.com/en/dai}
\bibitem{Munoz18} J. L. Muñoz. Docker Containers. Notes from masterclasses. Master’s degree in Blockchain Technologies. 1st Edition. UPC School. 29 November 2018.
\bibitem{Nakamoto08} S. Nakamoto. \textit{Bitcoin: A Peer-to-Peer Electronic Cash System}. 31 October 2008.  \href{https://bitcoin.org/bitcoin.pdf}{https://bitcoin.org/bitcoin.pdf}
\bibitem{RaspberryPi19} Raspberry Pi 3 Modelo B - Placa Base (1.2 GHz Quad-Core Arm Cortex-A53, 1 GB RAM, USB 2.0). Amazon. 11 August 2019.
\bibitem{RaspberryPiBuy19} Raspberry Pi FAQs. BUYING AND SHIPPING. Where can I buy a Raspberry Pi?. Official Web Page. 11 August 2019.  (\href{https://www.raspberrypi.org/help/faqs/#buyingWhere}{Link})
\bibitem{Stallings04} W. Stallings. \textit{Comunicaciones y redes de computadores}. 1 September 2004. 904 pages. Pearson Prentice Hall. ISBN-13: 978-8420541105.

\bibitem{berec16} Report on OTT services. BEREC (Body of European Regulators for Electronic Communications). January 2016.
\bibitem{eecc18} Directive (EU) 2018/1972 of the European
  Parliament and of the Council of 11 December 2018 establishing the
  European Electronic Communications Code (Recast)Text with EEA
  relevance. PE/52/2018/REV/1.

\bibitem{gdpr16} Regulation (EU) 2016/679 of the European
  Parliament and of the Council of 27 April 2016 on the protection of
  natural persons with regard to the processing of personal data and
  on the free movement of such data, and repealing Directive 95/46/EC
  (General Data Protection Regulation) (Text with EEA relevance).

\bibitem{h202018} Ethics and data protection. European
  Commission (DG Research and Innovation). 14 November 2018.

\bibitem{tata17} A Systematic Approach to Ensuring GDPR
    Compliance: Key Action Items for Telecom Operators. White
    Paper. Tata Consultancy Services. 2017.

\bibitem{neutral} Enabling Neutral Host
Network Economics: CCS case study, GSM Association. August 2018.
\end{thebibliography}
\clearpage
